Distanced-based VOCC analysis

### 2019-05-17 analysis/VOCC/dist-vocc.Rmd
test alternate data option

# add and scale predictors after filtering for survey(s) of interest
data <- all_depth$data %>%
  filter(depth_max>10) %>% # removes data if sensor stayed too near surface
  # filter(ssid != 1) %>%
  # filter(ssid != 3) %>%
  # filter(ssid != 4) %>%
  # filter(ssid != 16) %>%
  gfplot:::scale_survey_predictors()

@@

@@

nd <- rbind(nd_1, nd_3, nd_4, nd_16)
# nd <- nd_4 # for faster test option
nd <- nd %>% dplyr::mutate(shallow = ifelse(depth > 35, 0, 1))

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
# # choose the spatial range to model
dat <- data %>% dplyr::filter(year > 2003) #%>% filter(ssid == 4)
nd <- nd # %>% filter(ssid == 4)

@@

# stopifnot(m_temp$model$convergence == 0L)
# m_temp
# # Warning messages:
# #   1: In doTryCatch(return(expr), name, parentenv, handler) :
# #   restarting interrupted promise evaluation
# 
saveRDS(m_temp, file = "data/m_temp_allyears.rds")
```

Calculate predicted values
```{r}
m_temp <- readRDS("../VOCC/data/m_temp_allyears.rds")

# can also be filtered to include only year with multiple surveys 
# m_temp <- readRDS("../VOCC/data/m_temp_allpost2003.rds")
# nd <- nd %>% dplyr::filter(year > 2003)

>>>>

# add and scale predictors after filtering for survey(s) of interest
data <- all_depth$data %>%
  filter(depth_m>10) %>% # removes data if sensor stayed too near surface
  # filter(ssid != 1) %>%
  # filter(ssid != 3) %>%
  # filter(ssid != 4) %>%
  # filter(ssid != 16) %>%
  gfplot:::scale_survey_predictors()

@@

Or use old data 
```{r eval=FALSE}
data <- readRDS("../tmb-sensor-explore/data/sensor-data-processed.rds")
data <- data %>% mutate(depth = depth_m) %>% 
  filter(depth_m >10) %>% # removes data if sensor stayed too near surface
  gfplot:::scale_survey_predictors()

data <- data[data$fishing_event_id != 481861, ]
```

@@

nd <- rbind(nd_1, nd_3, nd_4, nd_16)
# nd <- nd_4 # for faster test option
nd <- nd %>% dplyr::mutate(shallow = ifelse(depth > 35, 0, 1))
```

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
# # choose the spatial range to model
dat <- data %>% dplyr::filter(year > 2003) %>% select(year, ssid, X, Y, temperature_c, depth_scaled, depth_scaled2)
nd <- nd #%>% filter(ssid == 4)

@@

# stopifnot(m_temp$model$convergence == 0L)
# m_temp
# # Warning messages:
# #   1: In doTryCatch(return(expr), name, parentenv, handler) :
# #   restarting interrupted promise evaluation
# 
# saveRDS(m_temp, file = "data/m_temp_post2003.rds")
saveRDS(m_temp, file = "data/m_temp_allyears.rds")
```

Calculate predicted values
```{r}
m_temp <- readRDS("../VOCC/data/m_temp_post2003.rds")
# m_temp <- readRDS("../VOCC/data/m_temp_allyears.rds")

# can also be filtered to include only year with multiple surveys 
# m_temp <- readRDS("../VOCC/data/m_temp_allpost2003.rds")
# nd <- nd %>% dplyr::filter(year > 2003)
nd <- nd # %>% filter(ssid == 4)
